DATA 605 Week 13

### 2019-04-24 DATA605/MSilva_Assign13.Rmd
More work

$$y=x^2-2x-2, y=x+2$$

>>>>

$$f(x)=x^2-2x-2, g(x)=x+2$$

First we will visualize the two lines.  The first is blue and the second is red.

```{r, echo=FALSE, warning=FALSE}
library(ggplot2)

fx <- function(x){x^2 - 2*x - 2}
gx <- function(x){x + 2}

ggplot(data = data.frame(x = 0), mapping = aes(x = x)) +
  stat_function(fun = gx, color="red") + 
  stat_function(fun = fx, color="blue") +
  geom_hline(yintercept = 0, color="black") +
  geom_vline(xintercept = 0, color="black") +
  xlim(-8, 8) +
  ylim(-8, 8) +
  theme(aspect.ratio=1)
```

The two points where the lines intersect are

$$x^2-2x-2 = x+2 \rightarrow x^2-3x -4 = 0\rightarrow(x+1)(x-4) = 0\rightarrow x = -1 \text{ and } 4$$

$$\int_{-1}^4{(x+2)-(x^2-2x-2)} \rightarrow (x^2+2x)-(\frac{x^3}{3}+x^2-2x)|_{-1}^4$$

```{r, comment=NA}
fx <- function(x){
  (x+2)-(x^2 - 2*x - 2)
}
integrate(fx, -1, 4)
```
